\section{Discussion}

The strongest conclusion supported by the updated evidence is that \repo\ now supports a credible edge-oriented research program for sEMG finger-intent decoding, not just a loose collection of model experiments. Another researcher or engineer can now trace the workflow from raw PhysioMio recordings through preprocessing, feature extraction, tensor adaptation, direct baselines, optimized CNN students, teacher references, transfer-learning summaries, and deployment-facing utilities without reconstructing the pipeline by hand.

The updated benchmark also changes the model-level interpretation. In the earlier draft, the work looked like a trade-off between an LSTM with balanced discrimination and a GNN with stronger recall-sensitive summaries. That story is now incomplete. Once the merged CNN student sweep is included, the strongest committed artifacts are compact convolutional models that outperform the older direct baselines on every headline metric while remaining small enough to fit the intended embedded setting after quantization. This is exactly the kind of shift that a project paper should capture.

The transfer-learning summaries point toward a second useful lesson. Healthy-to-impaired staging appears substantially more promising for the CNN branch than for the LSTM branch. That asymmetry may reflect architecture-specific robustness, optimization differences, or the way the shared feature representation interacts with each model family. The project does not yet include the ablations needed to explain the mechanism, but it does provide enough evidence to motivate transfer learning as a real research direction rather than a speculative aside.

The project's deployment story is also more coherent than before, but it is still incomplete. The codebase now includes teacher-ensemble distillation, threshold calibration, and latency benchmarking, and the student model sizes are explicitly framed around Raspberry Pi 5-class constraints. Those are meaningful steps toward embedded inference. However, the paper still cannot claim a validated deployment path because the committed artifact set does not yet include end-to-end Raspberry Pi measurements, power or thermal observations, or a reproducible distilled-student benchmark pack aligned with the rest of the evaluation tree.

Several limitations remain and should be read plainly. First, the benchmark still centers on a single dataset and one main preprocessing configuration, with no committed ablation package isolating the contribution of filtering, denoising, feature design, threshold choice, or graph connectivity. Second, the GNN implementation uses dense window graphs, which may not scale gracefully as sequence length grows. Third, the transfer-learning summaries are committed as high-level JSON rather than full rerunnable experiment bundles with harmonized plotting and checkpoint metadata. Fourth, the broader rehabilitation objective still lacks the evidence that matters most for translation: on-device timing, robust behavior across users and sessions, and human-subject evaluation of whether predicted intent meaningfully improves therapy.

Taken together, these limitations do not weaken the value of the current paper as a research manuscript for arXiv. They define the next layer of work. The clearest path forward is to push the same artifact discipline into distilled-student evaluation, Raspberry Pi 5 benchmarking, and broader cross-patient or cross-session validation so that the project can be connected to a fully supported deployment paper later.
