\section{Experiments}

\subsection{Dataset and split construction}

All benchmark artifacts analyzed in this paper come from the project's \physiomio\ processing path implemented in \repo~\citep{physiomio2026,psrrepo2026}. The loader searches raw parquet files, extracts contiguous movement segments, maps gesture labels to five-bit finger targets, preprocesses each segment, and stores processed tensors as PyTorch split files.

The split logic is patient-level rather than segment-level. Patients are shuffled with a fixed seed and divided into 70\% train, 10\% validation, and 20\% test partitions, which reduces identity leakage between train and test segments. The default loader configuration targets impaired-arm recordings unless the user explicitly changes the arm-split setting, so the main benchmark should be interpreted as an impaired-arm post-stroke decoding study. The two-stage transfer summaries use the same software pathway with healthy-arm pretraining followed by impaired-arm finetuning.

\subsection{Evidence scope}

The project exposes a richer experimental surface than a single comparison table. In addition to direct LSTM, CNN, and GNN runs, the implementation contains optimized CNN student and teacher evaluations, healthy-to-impaired pretraining and finetuning summaries, optional threshold tuning, teacher-ensemble distillation, and latency benchmarking. However, not all branches are represented by equally complete committed result bundles. This paper therefore separates three evidence tiers: direct committed test metrics, committed auxiliary summaries such as transfer learning and CNN evaluation sweeps, and code-only deployment utilities whose behavior is documented but whose outputs are not yet comprehensively committed.

The project has also evolved over time. Historical direct baselines remain under \texttt{metrics/}, while newer CNN outputs live under \texttt{models/CNN/evaluations/}. We keep both because they jointly show how the study matured from an initial cross-family benchmark into a stronger edge-oriented CNN branch. When a newer optimized artifact supersedes an older baseline, the paper says so explicitly rather than averaging across incompatible runs.

\subsection{Evaluation protocol}

The project defines the task as five-label multilabel classification with a nominal decision threshold of 0.5 on the held-out test split. For transparency, the metric implementation records both exact-match accuracy and finger-wise summaries, which is important because different models can trade precision for recall while achieving similar per-label correctness. The headline tables in this paper use the metrics as stored in the committed result files. Threshold-tuning utilities are described in the methods and discussion but are not used to create new manuscript numbers.

This paper follows an evidence-constrained writing policy. Every headline claim is tied to a committed code path, metric file, or project artifact. Because the current evidence base does not yet include a full ablation package, an on-device Raspberry Pi 5 benchmark log, or a polished distilled-student result bundle, we deliberately avoid module-level causality claims and instead focus on benchmark-level observations that are directly supported by saved outputs.
