\section{Introduction}

Finger-intent prediction from surface electromyography (sEMG) is an attractive interface for post-stroke neurorehabilitation because it offers a non-invasive path from residual muscle activity to assistive control, therapy feedback, and fine-motor retraining~\citep{munoznovoa2022upper,zheng2021semg}. In the broader PSR project, that decoding capability is intended to support compact machine-learning models that can ultimately be served on Raspberry Pi 5-class hardware and connected to a rehabilitation glove. This manuscript presents the software-facing research component of that agenda: the data-processing, modeling, and evaluation work that turns multichannel sEMG into five-finger intent predictions.

The challenge is not only raw predictive accuracy, but also methodological reproducibility. Post-stroke sEMG is noisy, patient-specific, and sensitive to recording conditions, so benchmark results depend heavily on how signals are filtered, denoised, segmented, labeled, tensorized, and split across patients. Reviews of sEMG-based gesture recognition consistently note that preprocessing design, feature representation, and real-time deployment constraints can matter as much as the final classifier family~\citep{li2021gesture,ni2024survey}. A research project that reports model performance without a stable preprocessing and evaluation path is therefore difficult to audit and even harder to extend toward embedded rehabilitation use.

\repo\ addresses that gap by providing the experimental framework for the project in one codebase~\citep{psrrepo2026}. The current implementation includes PhysioMio ingestion, gesture-to-finger label mapping, a fixed signal-conditioning stack, window-level feature extraction, tensor adapters, LSTM and GNN baselines, a merged 1D CNN student/teacher suite, Optuna-based hyperparameter optimization, healthy-to-impaired transfer-learning summaries, and benchmark artifacts stored as committed metric files. Recent project updates also added teacher-ensemble distillation, per-finger threshold tuning, and latency benchmarking utilities, which materially improve the edge-oriented experimental story even when the outputs of those utilities are not yet fully committed as benchmark bundles.

The central story of this paper is therefore project-oriented rather than repository-oriented. We do not present a new decoding architecture, nor do we claim that the current implementation already demonstrates end-to-end rehabilitation hardware validation. Instead, we report a research program whose current contribution lies in making experimental assumptions explicit: which recordings are used, how they are preprocessed, how tensors are shared across model families, which metrics are computed, and which deployment-facing hooks are already present in code.

This updated paper makes four project-level contributions. First, it formalizes the current experimental pipeline from PhysioMio ingestion through preprocessing, feature extraction, tensor adaptation, model fitting, and deployment-screening utilities. Second, it consolidates the current benchmark evidence into one research narrative, including the optimized CNN student sweep, teacher evaluations, legacy direct baselines, and transfer-learning summaries. Third, it identifies what the project now supports for edge-oriented experimentation, including compact student architectures, teacher-ensemble distillation, threshold calibration, and latency measurement. Fourth, it draws a careful boundary around what is still missing, especially committed distilled-student outputs, on-device Raspberry Pi 5 validation, broader external baselines, and clinical evidence.
